Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2015-03-12 draft.tex
Disable unnecessary macros, green -> normal

\DeclareMathOperator{\cov}{Cov}
%\DeclareMathOperator{\skew}{Skew}
\DeclareMathOperator{\kurt}{Kurt}

%% Draft Macros %%
\newcommand{\todo}[1]{{\color{red}\bf ToDo: #1}}
\newcommand{\danny}[1]{{\color{purple}#1}}
\newcommand{\fred}[1]{{\color{brown!85!black}#1}}
\newcommand{\marcin}[1]{{\color{cyan}#1}}
\newcommand{\citeneeded}{{\color{red}\bf [cite needed]}}
\newcommand{\add}[1]{\textcolor{green!85!black}{#1}}
\newcommand{\del}[1]{\textcolor{red!85!black}{#1}}

@@

\item The approximate multivariate Gaussian distribution of $\vecest{S}$
    allows easier and more \add{precise} transfer of the information in the
  data to interested theorists for more accurate fits of
  standard-model and new-physics parameters \cite{Altmannshofer:2013foa,
Descotes-Genon:2013wba,Beaujean:2013soa},
  or for more precise predictions of optimized observables; see e.g.,
  \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
    Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf} for definitions
  of such optimized observables in $B\to K^*\ell^+\ell^-$ decays,
  \cite{Faller:2013dwa} for application to the decay $B\to
  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables
  in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
  likelihood also approaches a multivariate Gaussian as $N \to
  \infty$, the two methods differ in their utility as input for
  theorists if $\widehat{\vec{S}}$ is not well
  inside the physical region. For example, suppose there are two
  angular observables that are constrained to a triangular region by
  phase-space or unitarity arguments as
  \begin{equation}
    \label{eq:constr-ex}
    |S_1| + S_2 \le 1, \, S_1 \in [-1,1],\, S_2 \in [0,1] \,.
  \end{equation}
  It may (and often does) happen in practice that $\widehat{\vec{S}}$
  is close or even outside the allowed region such that a significant
  part of the probability mass covers unphysical values. In a Bayesian
  fit, one would take $\mathcal{N}(\vecest{S} | \vec{S},
  \widehat{\Sigma})$ as the sampling distribution of the ``data'', and
  simply set a uniform prior on the triangle in the $\vec{S}$ plane
  defined by \refeq{constr-ex} to have a well defined problem. This
  could be trivially combined with other independent information in a
  global fit. Someone with a different physics model might have to
  consider a
  different physical region, and could incorporate it just as easily.\\

>>>>

\DeclareMathOperator{\cov}{Cov}

%% Draft Macros %%
%\newcommand{\todo}[1]{{\color{red}\bf ToDo: #1}}
%\newcommand{\danny}[1]{{\color{purple}#1}}
%\newcommand{\fred}[1]{{\color{brown!85!black}#1}}
%\newcommand{\marcin}[1]{{\color{cyan}#1}}
%\newcommand{\citeneeded}{{\color{red}\bf [cite needed]}}
%\newcommand{\add}[1]{\textcolor{green!85!black}{#1}}
%\newcommand{\del}[1]{\textcolor{red!85!black}{#1}}

@@

\item The approximate multivariate Gaussian distribution of $\vecest{S}$
    allows easier and more precise transfer of the information in the
  data to interested theorists for more accurate fits of
  standard-model and new-physics parameters \cite{Altmannshofer:2013foa,
Descotes-Genon:2013wba,Beaujean:2013soa},
  or for more precise predictions of optimized observables; see e.g.,
  \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
    Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf} for definitions
  of such optimized observables in $B\to K^*\ell^+\ell^-$ decays,
  \cite{Faller:2013dwa} for application to the decay $B\to
  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables
  in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
  likelihood also approaches a multivariate Gaussian as $N \to
  \infty$, the two methods differ in their utility as input for
  theorists if $\widehat{\vec{S}}$ is not well
  inside the physical region. For example, suppose there are two
  angular observables that are constrained to a triangular region by
  phase-space or unitarity arguments as
  \begin{equation}
    \label{eq:constr-ex}
    |S_1| + S_2 \le 1, \, S_1 \in [-1,1],\, S_2 \in [0,1] \,.
  \end{equation}
  It may (and often does) happen in practice that $\widehat{\vec{S}}$
  is close or even outside the allowed region such that a significant
  part of the probability mass covers unphysical values. In a Bayesian
  fit, one would take $\mathcal{N}(\vecest{S} | \vec{S},
  \widehat{\Sigma})$ as the sampling distribution of the ``data'', and
  simply set a uniform prior on the triangle in the $\vec{S}$ plane
  defined by \refeq{constr-ex} to have a well defined problem. This
  could be trivially combined with other independent information in a
  global fit. Someone with a different physics model might have to
  consider a
  different physical region, and could incorporate it just as easily.\\
